\section{Results}
In this section, the results are presented using tables and charts. Note that on some charts the vertical axis is base 10 logarithmic (for viewing purposes). The implementation of all the algorithms for all languages can be found in Appendix \ref{appendix:code}. The section is divided into two subsections. The purpose of this division is to illustrate the performance hit that each language takes when running on the CLR instead of their own native environments. This is one side of creating the scaling factor for each language.

\subsection{Native environments}
This section display the results for the tests made in each language native environment. As is illustrated in each subsection, these tests tend to do better performance wise than the corresponding tests in the .NET environment. Important to note is that these tests compare different Virtual Machines.

\input{chapters/new_testing_results/native_addition_operator}

\input{chapters/new_testing_results/native_insertion_sort}

\input{chapters/new_testing_results/native_merge_sort}

\subsection{.NET environment} \label{subsec:net_environment}
This section display the results for the tests made in each language when run in the .NET environment. The tests tend to perform poorer performance wise than the corresponding tests in the native environment. Important to note is that these tests are run on the same Virtual Machine, the Microsoft CLR.

\input{chapters/new_testing_results/net_language_overhead}

\input{chapters/new_testing_results/net_addition_operator}

\input{chapters/new_testing_results/net_insertion_sort}

\input{chapters/new_testing_results/net_merge_sort}

\subsection{The scaling factors}
This section displays the scaling factors in Table \ref{table:scaling_factors}. The values are calculated by the following formula:
\newline
\newline
\centerline{ \scalebox{1.4}{ $ \frac{Java \, or \, Python \, time}{C\# \, time} = scaling \, factor $ } }
\newline
\newline

\begin{table}[h]
     \begin{center}
          \begin{tabular} { >{\centering\arraybackslash}m{4cm} | >{\centering\arraybackslash}m{1cm} | >{\centering\arraybackslash}m{1cm} | >{\centering\arraybackslash}m{2cm} }
               \hline
               \textbf{}                                  & \textbf{C\#}     & \textbf{Java}           & \textbf{Python} \\ \hline
               \textbf{Addition Operator}        & 1.0                 & 1.27                      & 1.67 \\ \hline
               \textbf{Insertion Sort}               & 1.0                 & 1.31                      & 107.59 \\ \hline
               \textbf{Merge Sort}                  & 1.0                 & 1.27                      & 94.42 \\  \hline
          \end{tabular}
     \end{center}
     \caption{This table shows the scaling factors of each language based on the test results in Section \ref{subsec:net_environment}. Java has a very consistent result set, varying by a factor of only 0.04 while Python varies greatly.}
     \label{table:scaling_factors}
\end{table}

As the table shows the scaling factor for Java is consistently between 1.27 and 1.31 giving an average of 1.29. The values for Python vary greatly from 1.67 to 107.59 giving an average of 67.

