\chapter{Introduction}

\section{Problem Statement}

A common challenge for Valtech and other consulting companies is to recruit the right people.  The recruitment process in the IT business often involves several steps and can be very time consuming. This is due to the fact that knowledge and skill differ greatly from programmer to programmer and therefore a need to interview many people arises (just to find one that is deemed suitable for the job). 

The recruitment process usually involves some kind of test to assert the skill of the programmer.  The test is sometimes performed on paper (questionnaire) or on a white board. Both of these environments aren’t really suitable to program in, hence most programmers tend to do their work on computers with the assistance of a web browser and a suitable IDE. 

These two issues present a challenge in which the optimal solution would result in less time spent recruiting and at the same time asserting the skills of the programmers before an interview is considered.

\section{Goal}
The main goal was to evaluate a system which could satisfy the demands stated above. Thus, since no such system was present at Valtech, there was a need to first build the system and then evaluate it through test cases with performance and memory consumption in mind. The system would allow users to submit solutions to common programming problems and then have their code evaluated. Their code would have to have a limit on execution time since a ``good'' programmer would be able to solve problems efficiently. The results of this evaluation would be used to estimate how much time the different programming languages would need in order to solve specific problems, as all of these languages would be run in the Microsoft .NET Platform.

\section{About Valtech}
Valtech is an independent, global IT-consulting company with offices in Europe, United States and Asia. The company was founded 1993 in France and has over 1600 employees worldwide. The Swedish branch is primarily oriented towards web solutions. 
Valtech's most well-known award winning projects include the websites 1177.se, Antagning.se and Riksbank.se. 

All work concerning this thesis was carried out at Valtech in Stockholm, Sweden.






