\chapter{Method}
This chapter discusses the implementation details of the system.

\section{IKVM}
IKVM.NET is an implementation of Java for Mono and the Microsoft .NET Framework. It includes the following components:

\begin{itemize}
	\item A Java Virtual Machine implemented in .NET
	\item A .NET implementation of the Java class libraries
	\item Tools that enable Java and .NET interoperability
\end{itemize}

It also includes (among other things) a Java bytecode to .NET IL translator, which is what this project used to achieve its Java compatability.


\section{IronPython}
The website for IronPython describes it in the following way: ``IronPython is an open-source implementation of the Python programming language which is tightly integrated with the .NET Framework. IronPython can use the .NET Framework and Python libraries, and other .NET languages can use Python code just as easily.'' (Source: http://ironpython.net/)

\subsection{IronPython vs Python}

\subsubsection{The HelloWorld test}
This test simply prints ``Hello World''. In terms of performance, Python has a strong lead on IronPython. This would suggest that IronPython has quite the overhead (refer to later section about overhead testing).

Results
Python 2.7: 0.0677239 seconds
IronPython 2.7: 1.0527518 seconds

Source: http://ironpython.codeplex.com/wikipage?title=IP27A1VsCPy27Perf&referringTitle=IronPython%20Performance

\subsubsection{PyStone 1.1}
This test is just a rewrite of the Dhrystone test for the C programming language. In short the test intends to represent general processor performance by using integer only operations. 
Due to the fact that IronPython uses .NET Dynamic Language Runtime it can also use site caching. In short site caching basically remembers previous performed operations (i.e. a+b) which is why IronPython outperforms Python (might need reference to site caching here). 

Results
Python 2.7: 41187 PyStones/second
IronPython 2.7: 52101.1 PyStones/second

Source: http://en.wikipedia.org/wiki/Dhrystone
Source2: Source: http://ironpython.codeplex.com/wikipage?title=IP27A1VsCPy27Perf&referringTitle=IronPython%20Performance

\subsubsection{PyBench 2.0}
This is a collection of low level benchmarks. For example it tests string concatination and comparisons between different data types. More can be read at about the specific tests at [ref same as above]

Overall results: Python is 61.6\% faster than IronPython.

Source: Source: http://ironpython.codeplex.com/wikipage?title=IP27A1VsCPy27Perf&referringTitle=IronPython%20Performance

\section{About CELINE}

\section{Implementation}

\subsection{IKVM}

\subsection{IronPython}

