\section{Conclusion}
The goal of this thesis was to evaluate the performance of different languages run in the .NET environment. The results indicate that Python suffers from significant performance problems. One could argue that the problem is not Python but rather the tests. Sorting for instance is best handled using the built-in functions. However, if one was to apply for a job and the task was to implement sorting algorithms in order to demonstrate their programming proficiency, the recruiter would not have them use the built-in functions as this would not reveal whether the applicant understands how to implement the algorithm or not.

This thesis concludes that while implementing multiple language compatibility in .NET is possible it is not feasible for all languages with concerns to performance. See, for example, the time it takes for Python to sort 1 million elements in .NET using Merge sort (Figure \ref{fig:net_merge_sort}). The compensation times of the Python code varies considerably depending on how many built-in functions one can use or is allowed to use for solving a problem. This makes the task of obtaining a general scaling factor troublesome.

Benchmarking between different languages is very difficult to do fairly and no benchmark can give a just picture of what programming language is the ``best'' to use. It all depends on the needs of the project. Some languages are better at optimizing time spent programming (like Python or Ruby) while other languages specialize in optimizing processor time (like C or C++). Many languages tend to be somewhere in between (i.e. Java and C\#).

Instead of having .NET be the only back-end it could be used for handling input/output, security and then use separate processes for each language where this process simply executes the submitted code in its native language environment (e.g. Java code using \textit{java.exe} or Python code using \textit{python.exe}). This is the way many modern systems are built (see Section \ref{sec:todays_systems}), and for good reason. Using this approach however, would defeat the very purpose of this thesis.
